---
title: "Mini-Project 2"
author: "Michael Ulis, Ayla Orona, Maeric Barrows"
date: "2024-04-09"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## Front Matter
```{r loadPackages, message = FALSE, warning=FALSE}
#Load packages with groundhog to improve stability
library(tidyverse)
library(rvest)
library(ggplot2)
library(lubridate)
library(kableExtra)
```

## Read in Data Set/Data Wrangling - Michael

```{r}
COD1 <- read_html(
  x = "https://docs.google.com/spreadsheets/d/1Wv5dlzCYv37aY58MF9nuuYJbHRBWm_dQ/edit?usp=sharing&ouid=106338911046216482900&rtpof=true&sd=true"
) %>%
  html_elements(css = "table") %>%
  html_table()

COD1 <- COD1[[1]]

COD2 <- read_html(
  x = "https://docs.google.com/spreadsheets/d/1Ora5ZiTjb2qrmqPV6P1wh7CyJweHpw7NJ1kxXWVodfk/edit?usp=sharing"
) %>%
  html_elements(css = "table") %>%
  html_table()

COD2 <- COD2[[1]]

COD3 <- read_html(
  x = "https://docs.google.com/spreadsheets/d/1ZlUHg4408PpJlFJeXENcqujAI7LWRL0o8ElHciJNlEw/edit?usp=sharing"
) %>%
  html_elements(css = "table") %>%
  html_table()

COD3 <- COD3[[1]]

colnames(COD1) <- COD1[1,]

colnames(COD2) <- COD2[1,]

colnames(COD3) <- COD3[1,]

COD1 <- COD1[-1, ]

COD1 <- COD1[-1, ]

COD1 <- COD1[, -1]

COD2 <- COD2[-1, ]

COD2 <- COD2[, -1]

COD3 <- COD3[-1, ]

COD3 <- COD3[, -1]

COD3 <- COD3[-(14:99),]

COD <- full_join(COD1, COD2)

COD <- full_join(COD, COD3)

COD[COD == ""] <- NA

COD$Eliminations <- as.numeric(COD$Eliminations)

COD$Deaths <- as.numeric(COD$Deaths)

COD$Score <- as.numeric(COD$Score)

COD$TotalXP <- as.numeric(COD$TotalXP)

COD$Damage <- as.numeric(COD$Damage)

COD <- COD %>%
  separate(Result, c("YourScore", "OtherScore"))

glimpse(COD)
```

## 1. Why not na.omit()?

We would not want to use na.omit for this dataset because at least one instance of NA is present in every row. If we were to use na.omit, every single row would be removed from the table. The below function shows how many NAs are present in each row:

```{r}
countNA <- function(dat){
  numNA <- sum(is.na(dat))
  return(numNA)
}

# MARGIN = 1 allows this to countNA by row
apply(X = COD, MARGIN = 1, FUN = countNA)
```

## 2. 6 Visualizations

### Damage - Ayla Orona

```{r}
sum(is.na(COD$Damage))
```
There is 0 missing Damage data in the table.

```{r}
table_1 <- COD %>%
  summarize(mean = mean(Damage),
            median = median(Damage),
            StandardD = sd(Damage),
            min = min(Damage),
            max = max(Damage))

table_1

table_1 %>%
  kable(
    digits = 2,
    format.args = list(big.mark = ","),
    caption = "Summary Table for Damage per Game",
    col.names = c("Mean","Median", "Standard Deviation", "Minimum","Maximum"),
    booktabs = TRUE
  ) %>%
  kableExtra::kable_classic(lightable_options = "striped",
                            latex_options = c("scale_down", "HOLD_position"))
```

The variable Damage is quantitative data, meaning its type of data is only integers. For the Damage column, the mean is 415.16, the median is 397, the standard deviation is 166.31, the min is 56, and the max is 960.

```{r}
ggplot(data = COD, mapping = aes(x = Damage))+
  geom_histogram(color = "black", fill = "blue")
```

Based on the visualization we can learn from the distribution of Damage. Based on the histogram, in most instances Damage was between 250 and 500 per game.

### FullPartial - Ayla Orona

```{r}
sum(is.na(COD$FullPartial))
```

There is not missing data for the FullPartial column in the data set.

```{r}
table_2 <- COD %>%
  group_by(FullPartial)%>%
  summarise(N=n())
  
table_2 %>%
  kable(
    digits = 2,
    format.args = list(big.mark = ","),
    caption = "Summary Table for Game Length",
    col.names = c("Game Length", "Total Games Played"),
    align = c("l", rep("c", 2)),
    booktabs = TRUE
  ) %>%
  kableExtra::kable_classic(lightable_options = "striped",
                            latex_options = c("scale_down", "HOLD_position"))
```

Based on the summary statistics of the FullPartial column, we can determine that 191 instances were Full and 20 were partial.

```{r}
#full or partial based on eliminations
ggplot(data = COD, mapping = aes(x = FullPartial, y = Eliminations))+
  geom_boxplot()
```

Based on this visualization, we can see the differences in the amount of eliminations based on whether the game was full or partial. If the game was full, the elimination mean was 15, however, if it was partial, the mean was around 8. This could possibly due to the fact that because the player was playing a full game, their eliminations would increase because they had a longer amount of time of playing the game. 

### Game Type - Michael

```{r}
sum(is.na(COD$GameType))
```

There are no instances of NA in the GameType column.

```{r}
gt_table <- COD %>%
  group_by(GameType) %>%
  summarise(N = n()) %>%
  arrange(desc(N))

gt_table$GameType <- c("Team Death Match", "Hardpoint", "Domination", "Kill Confirmed")

gt_table %>%
  kable(
    digits = 2,
    format.args = list(big.mark = ","),
    caption = "Summary Table for Game Type",
    col.names = c("Map", "Total Games Played"),
    align = c("l", rep("c", 2)),
    booktabs = TRUE
  ) %>%
  kableExtra::kable_classic(lightable_options = "striped",
                            latex_options = c("scale_down", "HOLD_position"))
```

Based on the summary statistics of the GameType column, we can determine that 187 instances were Team Deathmatch and 8 were Hardpoint, 3 were Domination, and 3 were Kill Confirmed.

```{r}
gt_labs <- c("Domination", "Hardpoint", "Kill Confirmed", "Team Death Match")

ggplot(data = COD, mapping = aes(x = GameType, fill = GameType)) +
  geom_bar() + 
  labs(x = "Game Type", 
       y = "Games Played", 
       title = "Number of Games per Game Type",
       subtitle = "Call of Duty") +
  theme(
    plot.title = element_text(size = 16L,
                              face = "bold",
                              hjust = 0.5),
    plot.subtitle = element_text(size = 12L,
                                 hjust = 0.5),
    axis.title.x = element_text(size = 12),
    axis.title.y = element_text(size = 12),
    legend.position = "none") + 
    scale_x_discrete(labels= gt_labs)
```

This table and visualization help show the number of games played by this player for every game mode available in Call of Duty. As you can see, this player played Team Deathmatch significantly more than any other game mode.

### XPType - Maeric

```{r}
sum(is.na(COD$XPType))
```
There are no instances of NA in the XPType column.

```{r}
table_3 <- COD %>%
  group_by(XPType)%>%
  summarise(N=n())

table_3 %>%
  kable(
    digits = 2,
    format.args = list(big.mark = ","),
    caption = "Summary Table for XP Boost Type",
    col.names = c("XP Boost Type", "Total Games Played"),
    align = c("l", rep("c", 2)),
    booktabs = TRUE
  ) %>%
  kableExtra::kable_classic(lightable_options = "striped",
                            latex_options = c("scale_down", "HOLD_position"))
```

XPType is a categorical variable that seems to measure what kind of boost a player would get to their XP given they win the game. Based on these summary statistics, 129 games played had an XPType of 10% Boost, while the remaining 82 had the Double XP + 10% XPType.

```{r}
ggplot(data = COD, mapping = aes(x = XPType, y = Score))+
  geom_boxplot(fill="cyan") +
  labs(x = "XP Type")
```
This boxplot shows performance, based on Score, of games with 10% Boost XPType versus games with Double XP + 10% XPType. Using the graph, we can see that, in general, this player performs better in games with Double XP + 10% XPType.

### Map1 - Maeric

```{r}
sum(is.na(COD$Map1))
```
There are 43 instances of NA for the Map1 column.

```{r}
table_4 <- COD %>%
  group_by(Map1)%>%
  summarise(N=n()) %>%
  arrange(desc(N))

table_4 %>%
  kable(
    digits = 2,
    format.args = list(big.mark = ","),
    caption = "Summary Table for Map1",
    col.names = c("Map", "Total Games Played"),
    align = c("l", rep("c", 2)),
    booktabs = TRUE
  ) %>%
  kableExtra::kable_classic(lightable_options = "striped",
                            latex_options = c("scale_down", "HOLD_position"))
```

This summary table shows every different map in the Map1 column. According to this data, with the exception of NA, The Pines showed up as Map1 the most, with 12 occurrences, followed by Moscow, with 11.

```{r}
ggplot(data = COD, mapping = aes(x = Map1, fill = Map1)) +
  geom_bar() + 
  labs(x = "Map", 
       y = "Games Played", 
       title = "Number of Games per Map",
       subtitle = "Call of Duty") +
  theme(
    plot.title = element_text(size = 16L,
                              face = "bold",
                              hjust = 0.5),
    plot.subtitle = element_text(size = 12L,
                                 hjust = 0.5),
    axis.title.x = element_text(size = 12),
    axis.title.y = element_text(size = 12),
    axis.text.x = element_text(angle = 45, hjust=1), 
    legend.position = "none")
```

This graph further shows the times each map was Map1.

### Map2 - Michael

```{r}
sum(is.na(COD$Map2))
```
There are 43 instances of NA for the Map2 column.

```{r}
table_5 <- COD %>%
  group_by(Map2)%>%
  summarise(N=n()) %>%
  arrange(desc(N))

table_5 %>%
  kable(
    digits = 2,
    format.args = list(big.mark = ","),
    caption = "Summary Table for Map2",
    col.names = c("Map", "Total Games Played"),
    align = c("l", rep("c", 2)),
    booktabs = TRUE
  ) %>%
  kableExtra::kable_classic(lightable_options = "striped",
                            latex_options = c("scale_down", "HOLD_position"))
```

This summary table shows every different map in the Map1 column. According to this data, with the exception of NA, Crossroads Strike showed up as Map2 the most, with 12 occurrences, followed by Cartel and Yamantau which are tied at 10.

```{r}
ggplot(data = COD, mapping = aes(x = Map2, fill = Map2)) +
  geom_bar() + 
  labs(x = "Map", 
       y = "Games Played", 
       title = "Number of Games per Map",
       subtitle = "Call of Duty") +
  theme(
    plot.title = element_text(size = 16L,
                              face = "bold",
                              hjust = 0.5),
    plot.subtitle = element_text(size = 12L,
                                 hjust = 0.5),
    axis.title.x = element_text(size = 12),
    axis.title.y = element_text(size = 12),
    axis.text.x = element_text(angle = 45, hjust=1), 
    legend.position = "none")
```

This graph further shows the times each map was Map2.

## 3. Exploring Result Column
```{r}
# Getting Wins, Losses, and Ties
COD <- COD %>%
  mutate(Win = ifelse(YourScore < OtherScore, 1, 0),
         Loss = ifelse(YourScore > OtherScore, 1, 0),
         Tie = ifelse(YourScore == OtherScore, 1, 0))

# Winning%
winRatio <- sum(COD$Win)/nrow(COD)
# Losing%
lossRatio <- sum(COD$Loss)/nrow(COD)
# Tie%
tieRatio <- sum(COD$Tie)/nrow(COD)

winRatio
lossRatio
tieRatio
```

Win%: 0.4265403
Loss%: 0.5592417
Tie%: 0.01421801

## 4: Win or Lose Model
```{r}

model1 <- glm(Win ~ Eliminations + Deaths, family = binomial, data = COD)
summary(model1)
```

In this model, we are exploring the relationship between Win and Eliminations and Deaths. If 
eliminations increases by one then the percentage of winning increases by 10.9%. If your deaths increases by one winning decreases by 7.6%. 
